Manuscript Figures for Genome Biology

### 2018-09-05 manuscript_figures/manuscript_figures.Rmd
Adjust labels and legend of Figure S1

>>>>

## Figure contrasting FDR results in different yeast simulation settings

```{r Figure-yeast-pi0, fig.width = 10, fig.height = 8}
# strongly informative covariate (top panel)
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[(grepl("yeast-", objects) | grepl("yeastH-", objects) | 
                    grepl("yeastII-", objects) | grepl("yeastIIH-", objects)) & 
                   grepl("de5", objects) & 
                  !grepl("uninf", objects)] 
labs <- rep("30% Non-null", length(resfile))
labs[grepl("H", resfile)] <- "7.5% Non-null"
labs2 <- rep("Unimodal effect size", length(resfile))
labs2[grepl("II", resfile)] <- "Bimodal effect size"
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05")

plist <- vector("list", length(resfile))
tab <- NULL
for (l in seq_along(resfile)){

  de5 <- readRDS(file=resfile[l])
  res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))
  res5d$es_dist <- labs2[l]
  res5d$pi0 <- labs[l]
  tab <- rbind(tab, res5d)
}

FigStrong <- plotsim_average(tab, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE, grpVars = c("es_dist", "pi0")) +
                ggtitle("") +
  facet_grid( ~ es_dist + pi0) +
  ylim(0,0.3) 
FigStrong

# weakly informative covariate (bottom panel)
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[(grepl("yeastU-", objects) | grepl("yeastHU-", objects) | 
                    grepl("yeastIIU-", objects) | grepl("yeastIIHU-", objects)) & 
                   grepl("de5", objects) & 
                  !grepl("uninf", objects)] 
labs <- rep("30% Non-null", length(resfile))
labs[grepl("H", resfile)] <- "7.5% Non-null"
labs2 <- rep("Unimodal effect size", length(resfile))
labs2[grepl("II", resfile)] <- "Bimodal effect size"
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05")

plist <- vector("list", length(resfile))
tab <- NULL
for (l in seq_along(resfile)){

  de5 <- readRDS(file=resfile[l])
  res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))
  res5d$es_dist <- labs2[l]
  res5d$pi0 <- labs[l]
  tab <- rbind(tab, res5d)
}

FigWeak <- plotsim_average(tab, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE, grpVars = c("es_dist", "pi0")) +
                ggtitle("") +
  ylim(0,0.3) +
  facet_grid( ~ es_dist + pi0)
FigWeak

leg <- get_legend(FigStrong)
Fig <- plot_grid(FigStrong + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)), 
                 FigWeak + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)),
                 nrow = 2, 
                 labels = paste0(LETTERS[1:2], "       ",
                          c("Strongly informative covariate",
                            "Weakly informative covariate")),
                 hjust = 0)
plot_grid(Fig, leg, ncol=2, rel_widths = c(1,0.1))
ggsave(file.path(outdir, "Figure_yeast_varyingpi0.pdf"), width=10, height=6.5)
